Differential Expression - HBCC - DLPFC - Sex

### 2020-08-19 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd
revert

```{r knit2synapse, eval=FALSE}
render::rmarkdown("individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd")

@@

thisFileName <- 'HBCC_DLPFC_DE.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/',thisFileName))
```

>>>>

```{r knit2synapse, eval=FALSE}
ml git pandoc
rmarkdown::render("individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd")

@@

thisFileName <- 'HBCC_DLPFC_DE_Diagnosis.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/split_by_analysis/',thisFileName))
```

### 2020-08-19 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Sex.Rmd
revert

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)

@@

thisFileName <- 'HBCC_DLPFC_DE.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/',thisFileName))
```

>>>>

```{r knit2synapse, eval=FALSE}
ml git pandoc
rmarkdown::render("individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Sex.Rmd")

library(synapser)
library(knit2synapse)

@@

thisFileName <- 'HBCC_DLPFC_DE_Sex.Rmd'

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/split_by_analysis/',thisFileName))
```
